### 2015-07-02 thesis/thesis/chap6/chap6.tex
changes

Conclusion Conclusion Conclusion
%To conclude, we believe that the proposed framework
%********************************************************************
%* Section 7: Future Work
%********************************************************************
\section{Future Work}

@@

@@

>>>>

In this theses we proposed three models for aggregation of web services within communities. The goal of our models are to maximize efficiency by collaborating and forming stable communities. In our first contributions focus on stability and

\section{Future Work}

@@

\item F. Al-Saqqar, J. Bentahar, K. Sultan, W. Wan, E. Khosrowshahi Asl:, "Model checking temporal knowledge and commitments in multi-agent systems using reduction", Journal of Simulation Modelling Practice and Theory, 2015.

@@

\item B. Khoravifar, M. Alishahi, E. Khosrowshahi Asl, J. Bentahar, R. Mizouni, H. Otrok, "Analyzing Coopetition Strategies of Services within Communities", ICSOC, Shanghai, China, 2012

\item H. O. Marey, J. Bentahar, E. Khosrowshahi Asl, M. Mbarki, R. Dssouli, "Agents' Uncertainty in Argumentation-based Negotiation: Classification and Implementation", ANT/SEIT, Hasselt, Belgium, 2014.

\item H. Fallatah, J. Bentahar, E. Khosrowshahi Asl, "Social Network-Based Framework for Web Services Discovery", IEEE  FiCloud, Barcelona, Spain, 2014.
